Assessment and optimization of respiratory syncytial virus prophylaxis regimens in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}

### 2020-07-20 paper/structure.tex
Fixing case sensitivity
Fit abstract on page 1
Really fit abstract on page 1
Bibliography inlining
Switched from biblatex to bibtex
https://tex.stackexchange.com/questions/12175/biblatex-submitting-to-a-journal

\usepackage[backend=bibtex,style=nejm,sorting=none,autocite=superscript,articledoi=true,url=false]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)
%\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)
\usepackage[nottoc]{tocbibind}

\addbibresource{../RSVOptimization.bib} % The filename of the bibliography
\renewcommand{\cite}[1]{\autocite{#1}}

\usepackage[autostyle=true]{csquotes} % Required to generate language-dependent quotes in the bibliography

>>>>

\bibliographystyle{ama}
